\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
finished working on intro

\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

\paragraph {Our Contributions}
We first study whether improvements are possible by relaxing the definition of the main building block of fuzzy extractors, called \emph{secure sketch}.  A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$ (The key $r$ is formed by the fuzzy extractor by applying a randomness extractor~\cite{nisan1993randomness} to $w$.)  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.

The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.  We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.  
%Furthermore, we have (asymptotic)~constructions that meet these bounds.

Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.  Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.  We show lower bounds on the unpredictability loss of sketches.  We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.

Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.  To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.  
\lnote{stopped here}

%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high. 
The minimum entropy loss for secure sketches has been quantified in past work.  Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}, 
%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
the entropy loss of a secure sketch that can reconcile $t$ errors
 %with high probability 
 is bounded by the redundancy of
the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  Constructions of fuzzy extractors that use a secure sketch inherit this bound.
%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).

To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.  Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.

On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.  We show that some entropy loss is necessary for secure sketches.

@@

By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{As noted above, using a computational extractor, in place of a information-theoretic extractor, allows a lossless construction.  However, this approach requires the computational extractor to work on the remaining entropy after the secure sketch.  We compare the two approaches in \secref{sec:prg based comparison}}. % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).  
Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.  
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.  To apply the LWE assumption, we correct errors of a random linear code which limits our decoding algorithm to reconciling a logarithmic number of differences.

@@

\textbf{Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal in the setting without errors.  One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.  In particular, one technique is \emph{extract-then-expand}, where the output of a randomness extractor is stretched using a pseudorandom generator.  This construction is only possible if the entropy loss due to a secure sketch leaves enough truly random bits.  
%We ask whether it is possible to avoid this loss by making whole process ``computational.''
We compare the two approaches in \secref{sec:prg based comparison}.

>>>>

\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

\paragraph {Our Negative Results}
We first study whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.  A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.  This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors get random strings from strings with conditional min-entropy.

The most natural relaxation of the min-entropy requirement of the secure sketch is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, we could still use a randomness extractor to obtain $r$ from $w$, because it would yield a pseudorandom key.  Unfortunately, it is unlikely that such a relaxation will yield fruitful results: we prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.  
%Furthermore, we have (asymptotic)~constructions that meet these bounds.

Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$. This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).  Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$, which (for high-entropy sources of $w$ over the Hamming metric) matches the best information-theoretic security sketches.

%%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high. 
%The minimum entropy loss for secure sketches has been quantified in past work.  Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}, 
%%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
%the entropy loss of a secure sketch that can reconcile $t$ errors
% %with high probability 
% is bounded by the redundancy of
%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  Constructions of fuzzy extractors that use a secure sketch inherit this bound.
%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).

@@

\paragraph {Our Postive Results}

Both of the above negative results arise because a secure sketch functions like a decoder of an error-correcting code.  To avoid them, we give up on building computational secure sketches and focus directly on the entropy loss in fuzzy extractors.  Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.

By considering this computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$. % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).  
Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.  
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.  To apply the LWE assumption, we correct errors of a random linear code, which limits our decoding algorithm to reconciling a logarithmic number of differences.

@@

\paragraph{An Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal of obtaining a pseudorandom key $r$ from a source $w$ in the setting without errors.  They can be constructed, for example, by applying to pseudorandom generator to the output of an information-theoretic extractor.  One way to build a computational \emph{fuzzy} extractor is by using a computational extractor instead  of the information-theoretic extractor in the construction of  \cite{DBLP:journals/siamcomp/DodisORS08}.   However, this approach is possible only if conditional min-entropy of $w$ conditioned on the sketch $s$ is high enough.  
%We ask whether it is possible to avoid this loss by making whole process ``computational.''
We compare the two approaches in \secref{sec:prg based comparison}.
